---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(knitr)
```

# MVSE

MVSE, Mosquito-borne Viral Suitability Estimator, provides methods for the estimation of an index of climate-based transmission potential for mosquito-borne viruses. It can be parameterized for any combination of host, virus and mosquito-species of interest with local climate data. 

## Installation

The MVSE package is currently not hosted on CRAN (Comprehensive R Archive Network). We thus need to install the package directly from the GithHub repo where it is hosted. 

```{r results='hide', message=FALSE}
install.packages("devtools")
install.packages("tidyverse")
require(tidyverse)
require(devtools)

install_github("TaishiNakase/MVSE")
```

## Example

Let's go through a short example of how one might use MVSE to estimate Index P for some mosquito-borne virus. 

First, we will install some packages. 

```{r message=FALSE}
library(MVSE)
```

We first need to create a `mvse_model` object, which requires time series data for climatic variables (i.e. temperature, humidity and rainfall) as well as epi-entomological prior distributions for the virus/vector/host system of interest. 

```{r}
# climate data
data("climateFSA")

# user-defined model
priors <- list(mosq_life_exp=list(pars=c(mean=12, sd=2), dist="normal"),
               mosq_inc_per=list(pars=c(mean=7, sd=2), dist="normal"),
               mosq_biting_freq=list(pars=c(mean=0.25, sd=0.01), dist="normal"),
               human_life_exp=list(pars=c(mean=71.1, sd=2), dist="normal"),
               human_inc_per=list(pars=c(mean=5.8, sd=1), dist="normal"),
               human_inf_per=list(pars=c(mean=5.9, sd=1), dist="normal"))
example_mvse_model <- mvse_model(model_name="user_test", climate_data=climateFSA, priors=priors)
```

Let's take a look at the input data to be used in the sampling procedure. 

```{r}
example_mvse_model
```

Next, let's perform the MCMC (Markov chain Monte Carlo) sampling procedure to estimate Index P. 

```{r}
example_mvse_fit <- sampling(example_mvse_model, verbose=FALSE)
```

Finally, let's take a look at the estimated distribution of the time series of Index P. 

```{r}
indexP_plot <- mcmc_index_dist(example_mvse_fit, index="indexP")
```
